### 2019-01-04 revisions/review-responses.tex

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

@@

		        Protactinium presents a challenge, since it has a large absorption cross 
				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
				 would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
				and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
				Accordingly, $^{233}$Pa is continuously 
				removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
				to decay to $^{233}$U without negative impact on neutronics.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 3: ``cycle time'' is not defined in the paper. Please 
        add.
        \begin{solution}
		        The ``cycle time'' definition has been added in a first appearance in text.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 224. The 3 day time step as the ``optimum'' for 
        Th fuel cycles in an MSR was first described and concluded by Powers et 
        al. Please add a reference to their initial work.
        \begin{solution}
        		The reference to \cite{powers_new_2013} has been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 234 onwards: Doesn't SERPENT already have an 
        MSR removal capability? If so, what is different about using SaltProc 
        with SERPENT?
        \begin{solution}
                It does. We tried use it before but these capabilities needs
                 to be verified. Additional text to clarify this point has 	
                been added to solution for question 21.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, Figure 7: The figure is hard to interpret or see 
        clearly what is going on. Could an additional figure or a zoomed in 
        portion be added to show what the swing in k is over a much shorter 
        time interval? k seems to be swinging dramatically but over what time 
        period and how would this be controlled in reality? The graph almost 
        suggests that the core is unstable??
        \begin{solution}
                Zoomed portion for 150 EFPD interval has been added. We also 
                added notes on a plot to explain swing in multiplication factor.
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 18, line 327: Are those elements removed every 3435 
        days, or is it that the entire salt core is discharged?
        \begin{solution}
		        100 \% of those elements atoms removed every 3435 days. Full salt discard
		         as it mentioned in Table 3 has not been implemented. More detailed 
		         explanation of this has been added:

		        Additionally, the presence of rubidium, strontium, cesium, and barium in
		         the core are disadvantageous to reactor physics. In fact, SaltProc fully 
		         removes all these elements every 3435 days (not a small mass fraction 
		         every 3 days) which causes the multiplication factor to jump by 
		        approximately 450 pcm, and limits using the batch approach for online 
		        reprocessing simulations. In future versions of SaltProc this drawback 
		        will be eliminated by removing elements with longer cycle times (seminoble 
		        metals, volatile fluorides, Rb, Sr, Cs, Ba, Eu) using different approach. 
		        Only mass fraction (calculated separately for each reprocessing group) 
		        will be removed every depletion step (e.g. 3 days) instead of removing 
		        100\% of element atoms after cycle time. 
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for 
                publication-to-publication comparison (e.g. Park \emph{et al.} and 
                Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

@@

                ...the total temperature coefficient of reactivity is relatively large and
                 negative during reactor operation (comparing with conventional PWR which 							temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ -3.08 pcm/K 							\cite{forget_integral_2018}), despite positive MTC, and affords excellent 
                 reactor stability and control.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 27, section 3.8: It needs to be made more clear that 
        these results were calculated, and that they are taken from the code 
        output.
        \begin{solution}
                This has now been clarified in the text:

                Table 7 summarizes the six factors for both initial and 
				equilibrium fuel salt composition. These factors and their statistical 								uncertainties have been calculated using SERPENT2 code for initial fuel salt 
				composition (see Table 2) and for equilibrium salt composition which was 
				obtained with SaltProc. 
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 29, Figure 15: Similar comment to above regarding Fig 7 
        - the results are difficult to see and interpret with such notable 
        swings.
        \begin{solution}
                Zoomed portion for 150 EFPD interval and clarifying 
                notes has been added.
        \end{solution}

### 2019-01-04 revisions/review-responses.tex

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Modeling and Simulation of Online Reprocessing in the Thorium-Fueled 
        Molten Salt Breeder Reactor\\
\large Response to Review Comments}
\author{Andrei Rykhlevskii, Jin Whan Bae, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which certainly improved the paper.

\begin{questions}
        \section*{Reviewer 1}

        \question Overall, a well written article in a topic area of interest 
        to a number of audiences. Technically very good, well written in the 
        description and analysis.  Well done authors!

        A few minor comments/suggestions/clarifications as follows:
        \begin{solution}
                Thank you for these kind comments. Your suggestions have 
                certainly improved the paper. 
        \end{solution}

        \question  Abstract: Given the recent announcement about TransAtomic 
        Power, you may want to remove them from your list?
        \begin{solution}
        		Thank you for your kind review. The current manuscript was submitted before 
		        announcement that TransAtomic is ceasing operations. It is removed from 
                        the list of MSR startups (indeed, the whole list was 
                        removed based on a comment by another reviewer).
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Table 1, page 3: SCALE/TRITON is fast as well as thermal 
        reactor capable.  
        \begin{solution}
		        Thank you for the recommendation. In Table 1 ``thermal'' has been changed 
		        to ``thermal/fast''.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 48: Should read ``...and refill using a single 
        or multiple unit cell ....''
        \begin{solution}
        		That statement has been modified as requested.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 4, Line 55. Also worth noting that the latest SCALE 
        release will have the same functionality using continuous removal (B. 
        R. Betzler, J. J. Powers, N. R. Brown, and B. T. Rearden, ``Molten Salt 
        Reactor Neutronics Tools in SCALE,'' Proc. M\&C 2017 - International 
        Conference on Mathematics \& Computational Methods Applied to Nuclear 
        Science and Engineering, Jeju, Korea, Apr. 16-20 (2017).)
        \begin{solution}
		        Thank you for the update. This sentence has been added:

		        ``The latest SCALE release will also have the same functionality using 
        		truly continuous removals \cite{betzler_implementation_2017}.''
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 8, Fig 2: Appears the image is cut off at the top?
        \begin{solution}
        The image has been replotted.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 13, line 209: The description of the Pa removal, 
        although correct, isn't quite fully correct. The reason the Pa is 
        removed from the core and hence flux is to then enable the Pa to decay 
        to U233. If it was left in the core, it would transmute further and 
        hence not be able to produce the U233 that is necessary for this 
        breeding cycle to work.
        \begin{solution}
        		Thanks for catching this. The following passage has been added:

		        ``Protactinium presents a challenge, since it has a large absorption cross 
				section in the thermal energy spectrum. Moreover, $^{233}$Pa left in the core
				 would produce $^{234}$Pa and $^{234}$U, which both are not useful as fuel, 
				and smaller amount of $^{233}$Pa would decays into the fissile $^{233}$U.
				Accordingly, $^{233}$Pa is continuously 
				removed from the fuel salt into a protactinium decay tank to allow $^{233}$Pa 
				to decay to $^{233}$U without negative impact 
                                on neutronics.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 3: ``cycle time'' is not defined in the paper. Please 
        add.
        \begin{solution}
                        The ``cycle time'' definition has been added at the first 
                        appearance in text. 
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 14, line 224. The 3 day time step as the ``optimum'' for 
        Th fuel cycles in an MSR was first described and concluded by Powers et 
        al. Please add a reference to their initial work.
        \begin{solution}
        		The reference to \cite{powers_new_2013} has been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 14, line 234 onwards: Doesn't SERPENT already have an 
        MSR removal capability? If so, what is different about using SaltProc 
        with SERPENT?
        \begin{solution}
                It does. Indeed, much of the inspiration for SaltProc was the 
                lack of documentation, difficulty of use, and various 
                inexplicable results we acquired when we tried use this 
                built-in capability. This capability has not performed well and 
                needs to be better documented and more robustly verified before 
                we can use it. We fully intend to contribute to its improvement 
                if it can be made to agree with expectations.  Additional text 
                to clarify this point has been add to solution for question 
                \ref{built-in}.                
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 18, Figure 7: The figure is hard to interpret or see 
        clearly what is going on. Could an additional figure or a zoomed in 
        portion be added to show what the swing in k is over a much shorter 
        time interval? k seems to be swinging dramatically but over what time 
        period and how would this be controlled in reality? The graph almost 
        suggests that the core is unstable??
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 18, line 327: Are those elements removed every 3435 
        days, or is it that the entire salt core is discharged?
        \begin{solution}
		        100 \% of those elements atoms are removed every 3435 
                        days. Full salt discard
		         as it mentioned in Table 3 has not been implemented. More detailed 
		         explanation of this has been added:

                        ``Additionally, the presence of rubidium, strontium, cesium, and barium in the
                        core are disadvantageous to reactor physics.
                        Overall, the effective multiplication factor gradually decreases from 1.075 to
                        $\approx$1.02 at equilibrium after approximately 6 years of irradiation.

                        In fact, SaltProc fully removes
                        all of these elements every 3435 days (not a small mass fraction every 3 days)
                        which causes the multiplication factor to jump by approximately 450
                        pcm, and limits using the batch approach for online reprocessing simulations.
                        In future versions of SaltProc this drawback will be eliminated by removing
                        elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
                         Cs, Ba, Eu). In that approach, chemistry models will inform separation
                         efficiencies for each reprocessing group and removal will optionally be spread more
                         evenly accross the cycle time.''
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 19, Figure 8 (and same for Fig 9): y-axis in grams/kgs 
        or mass units would be better for the reader.
        \begin{solution}
                Thank you for the recommendation. Atom density was chosen for publication-to-						publication comparison (e.g. Park \emph{et al.} and Betzler \emph{et al.}
                \cite{park_whole_2015, betzler_molten_2017}). Although mass would certainly 
                be more understandable for the reader and will be added in a future releases.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 20, Fig 9: What are the wiggles and dips , especially 
        seen for Np235?
        \begin{solution}
		        Explanation of this phenomenon has been added as follows:

                          ``Small dips in neptunium and plutonium number density 
                          every 16 years are caused by removing $^{237}$Np and 
                          $^{242}$Pu (included in Processing group ``Higher 
                          nuclides'', see Table~\ref{tab:reprocessing_list}) 
                          which decays into $^{235}$Np and $^{239}$Pu, 
                          respectively.''
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 20, line 351: It is more than just the Pu isotopes that 
        makes the spectrum harder? What about the other MAs etc?
        \begin{solution}
        		Thank you for the excellent point. The corrected sentence reads thus:

                         ``The neutron energy spectrum at equilibrium is harder 
                         than at startup due to plutonium and other strong 
                         absorbers accumulation in the core during reactor 
                         operation.''
        \end{solution}

        %---------------------------------------------------------------------
        \question  Fig 12: units on y-axis?
        \begin{solution}
                Thanks for catching this. The units $\frac{n}{cm^2 s}$ have been added.
        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 24, line 389: Should that be ``233U'' and not ``233Th''?
        \begin{solution}
u                Yes, we meant $^{233}$U production. The typo has been fixed. 
                Thanks so much for catching it!
        \end{solution}

        %---------------------------------------------------------------------
        \question  Table 5: Please provide some comments on the uncertainties - 
        where do they come from? Also, the ``reference'' results need to state 
        whether ``initial'' or ``equilibrium''
        \begin{solution}
                In Table 5, we added information in the reference column 
                containing data for initial fuel salt composition. Details 
                about uncertainties have been added:

                ``Table 5 summarizes temperature effects on reactivity calculated 
                in this work for both initial and equilibrium fuel 
                compositions, compared with the original \gls{ORNL} report data 
                \cite{robertson_conceptual_1971}.  By propagating the $k_{eff}$  
                statistical error provided by SERPENT2, uncertainty for each 
                temperature coefficient was obtained and appears in Table 5. 
                Other sources of uncertainty are neglected, such as cross 
                section measurement error and approximations inherent in the 
                equations of state providing both the salt and graphite density 
                dependence on temperature.''

        %---------------------------------------------------------------------
        \question  Page 26, line 425: ``Relatively large'' compared with what? 
        Perhaps results for an LWR case would be a good basis for comparison?
        \begin{solution}
                The sentence has been extended as follows:

                ...the total temperature coefficient of reactivity is 
                relatively large and negative during reactor operation 
                (comparing with conventional PWR which 							
                temperature coefficient about -1.71 pcm/$^\circ$F $\approx$ 
                -3.08 pcm/K 							
                \cite{forget_integral_2018}), despite positive MTC, and affords 
                excellent reactor stability and control.

                The moderator
temperature coefficient (MTC) is positive for the startup composition and decreases
during reactor operation because of spectrum hardening with fuel depletion.
Finally, the total temperature coefficient of reactivity is negative for both
cases, but decreases during reactor operation due to spectral shift. In
summary, even after 20 years of operation the total temperature coefficient of
reactivity is relatively large and negative during reactor operation (comparing
with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F
$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and
affords excellent reactor stability and control.

@@

                The moderator
temperature coefficient (MTC) is positive for the startup composition and decreases
during reactor operation because of spectrum hardening with fuel depletion.
Finally, the total temperature coefficient of reactivity is negative for both
cases, but decreases during reactor operation due to spectral shift. In
summary, even after 20 years of operation the total temperature coefficient of
reactivity is relatively large and negative during reactor operation (comparing
with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F
$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and
affords excellent reactor stability and control.

        \end{solution}

        %---------------------------------------------------------------------
        \question  Page 27, section 3.8: It needs to be made more clear that 
        these results were calculated, and that they are taken from the code 
        output.
        \begin{solution}
                This has now been clarified in the text:

                ``Table~7 summarizes the six factors for both initial and 
                equilibrium fuel salt composition. Using SERPENT2 and SaltProc, 
                tese factors and their statistical uncertainties have been 
                calculated for both initial and equilibrium fuel salt 
                composition (see Table~2).''
        \end{solution}

@@

        %---------------------------------------------------------------------
        \question  Page 29, Figure 15: Similar comment to above regarding Fig 7 
        - the results are difficult to see and interpret with such notable 
        swings.
        \begin{solution}
                <++>
        \end{solution}

        %---------------------------------------------------------------------

        \section*{Reviewer 2}

        %---------------------------------------------------------------------
        \question The paper presents a python script (SaltProc) that can 
        complement the Serpent 2 code capabilities in terms of fuel cycle 
        analysis of MSRs. The paper is well written and the tool might be 
        useful for the nuclear engineering community. However, before 
        publishing the paper, I recommend some revisions.
        \begin{solution}
                Thanks very much for these comments. We appreciate your 
                detailed review, which has certainly improved the paper.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question \label{built-in} The most critical point of the work is that the built-in 
        capabilities for online reprocessing of Serpent 2 have not been used. 
        Their use is mentioned in the future work, but it is not clear why 
        these capabilities have not been used in the current work. To the 
        author's knowledge, they have been available in Serpent 2 since quite a 
        while. The authors should clarify this point at the beginning of the 
        paper, and not only in the ``Future work'' section. Even though the 
        technical work was done without using these capabilities, they should 
        highlight what  SaltProc adds to the built-in Serpent capabilities, and 
        they should at least try to extrapolate on the potential advantages of 
        combining  SaltProc and Serpent capabilities. Based on this, they 
        should slightly restructure the paper in order to prove the claimed 
        advantages over Serpent 2.
        \begin{solution}
                Thank you for your helpful review. We tried to use these capabilities 
                \cite{rykhlevskii_online_2017} but have had a number of issues which 
                are hard to resolve due to lack of documentation and 
                published verifications of this feature. The following 
                paragraph has been added to clarify why these capabilities have 
                not been used in current work:

                ``Aufiero \emph{et al.} added an undocumented feature to SERPENT2 
                using a similar methodology by explicitly introducing 
                continuous reprocessing in the system of Bateman equations and 
                adding effective decay and transmutation terms for each nuclide 
                \cite{aufiero_extended_2013}. This was employed to study the 
                material isotopic evolution of the 
                \gls{MSFR}\cite{aufiero_extended_2013}. The developed extension 
                directly accounts for the effects of online fuel reprocessing 
                on depletion calculations and features a reactivity control 
                algorithm. The extended version of SERPENT2 was assessed 
                against a dedicated version of the deterministic ERANOS-based 
                EQL3D procedure in \cite{ruggieri_eranos_2006, 
                fiorina_investigation_2013} and adopted to analyze the 
                \gls{MSFR} fuel salt isotopic evolution.

                We employed this built-in SERPENT2 feature for a simplified 
                unit-cell geometry of the thermal spectrum thorium-fueled 
                \gls{MSBR} and found it unusable\footnote{ Some challenges in 
                no particular order: mass conservation is hard to achieve; 
                three types of mflow cards (0, 1 or 2) are indistinguishable in 
                purpose; an unexplained difference between CRAM and TTA 
                results; etc.}. Primarily, it is undocumented, and the 
                discussion forum for SERPENT users is the only useful source of 
                information at the moment. Additionally, the reactivity control 
                module described in Aufiero \emph{et al.} is not available in 
                the latest SERPENT 2.1.30 release. Third, the infinite 
                multiplication factor behavior for simplified unit-cell model 
                obtained using SERPENT2 built-in capabilities 
                \cite{rykhlevskii_online_2017} does not match with exist 
                MCNP6/Python-script results for the similar model by Jeong and 
                Park\footnote{ In our study k$_{\infty}$ drops from 1.05 to 
                1.005 during a 1200 days of depletion simulation while in Jeong 
                and Park work this parameter decreasing slowly from 1.065 to 
                1.05 for the similar time-frame.} 
                \cite{jeong_equilibrium_2016}. Finally, only two publications 
                \cite{aufiero_extended_2013, ashraf_nuclear_2018} using these 
                capabilities are available, reflecting the reproducibility 
                challenge inherent in this feature.

                If these challenges can be overcome through verification 
                against ChemTriton/SCALE as well as this work (the 
                SaltProc/SERPENT2 package), we hope to employ this SERPENT2 
                feature for removal of fission products with shorter residence 
                time (e.g., Xe, Kr), since these have a strong negative impact 
                on core lifetime and breeding efficiency.''

@@

        \end{solution}

        %---------------------------------------------------------------------

        \question In addition to this major point, I would suggest a few other 
        revisions. Considering the scope of the journal, mentioning the names of 
        companies and start-up is not appropriate. I would suggest removing 
        them.
        \begin{solution}
                The names of companies have been removed.
        \end{solution}

@@

        %---------------------------------------------------------------------

        \question The sentence ``Immediate advantages over traditional, solid-fueled, 
        reactors include near-atmospheric pressure in the 15 primary loop, 
        relatively high coolant temperature, outstanding neutron economy, 
        improved safety parameters,'' may suggest improved neutron economy vs 
        solid-fuel fast reactors. This is rarely the case, especially vs 
        Pu-based SFRs. I would suggest reformulating.
        \begin{solution}
                Thank you for the exceptional recommendation. The sentence has 
                been split into two, as follows:

                Immediate advantages over traditional commercial reactors 
                include near-atmospheric pressure in the primary loop, 
                relatively high coolant temperature, outstanding neutron 
                economy, and improved safety parameters. Advantages over 
                solid-fueled reactors in general include reduced fuel 
                preprocessing and the ability to continuously remove fission 
                products and add fissile and/or fertile elements 
                \cite{leblanc_molten_2010}.

@@

        %---------------------------------------------------------------------

### 2019-01-04 results.tex
done with review responses edits

\subsection{Fuel salt composition dynamics}
The analysis of the fuel salt composition evolution provides more comprehensive 
information about the equilibrium state. Figure~\ref{fig:adens_eq} shows the number 
densities of major nuclides which have a strong influence on the reactor core 
physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
the fuel salt change insignificantly after approximately 2500 days of operation. 
In particular, the $^{233}$U number density fluctuates by less than 0.8\% between
 16 and 20 years of operation. Hence, a quasi-equilibrium state was 
achieved after 16 years of reactor operation.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
  \caption{Number density of major nuclides during 60 years of reactor 
  operation.}
  \label{fig:adens_eq}
\end{figure}
In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), kept accumulating 
in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
isotopes in the core. In the end of the considered operational time, the core 
contained significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Small dips 
in neptunium and plutonium number density every 16 years are caused by removing
$^{237}$Np, $^{242}$Pu (included in Processing group ``Higher nuclides'', see
 Table~\ref{tab:reprocessing_list}) which decays into $^{235}$Np, $^{239}$Pu, 
 respectively. Thus, 
production of new fissile materials in the core, as well as $^{233}$U breeding, 
made it possible to compensate for negative effects of strong absorber 
accumulation and keep the reactor critical.
\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{fissile_short.png}
  \caption{Number density of fissile in epithermal spectrum nuclides 
  accumulation during the reactor operation.}
  \label{fig:fissile_short}
\end{figure}

@@

The fuel temperature coefficient (FTC) is negative for both initial and 
equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
capture cross sections in the thorium. A small positive effect of fuel density on 
reactivity increases from $+1.21$ pcm/K at reactor startup to $+1.66$ pcm/K for 
equilibrium fuel composition which has negative effect on FTC magnitude during the 
reactor operation. This is in good agreement with earlier 
research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
temperature coefficient (MTC) is positive for the startup composition and decreases 
during reactor operation because of spectrum hardening with fuel depletion. 
Finally, the total temperature coefficient of reactivity is negative for both 
cases, but decreases during reactor operation due to spectral shift. In 
summary, even after 20 years of operation the total temperature coefficient of 
reactivity is relatively large and negative during reactor operation (comparing 
with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F 
$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and 
affords excellent reactor stability and control.

>>>>

\subsection{Fuel salt composition dynamics}
The analysis of the fuel salt composition evolution provides more comprehensive 
information about the equilibrium state. Figure~\ref{fig:adens_eq} shows the number 
densities of major nuclides which have a strong influence on the reactor core 
physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
the fuel salt change insignificantly after approximately 2500 days of operation. 
In particular, the $^{233}$U number density fluctuates by less than 0.8\% between
 16 and 20 years of operation. Hence, a quasi-equilibrium state was 
achieved after 16 years of reactor operation.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
  \caption{Number density of major nuclides during 60 years of reactor 
  operation.}
  \label{fig:adens_eq}
\end{figure}
In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), kept accumulating 
in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
isotopes in the core. In the end of the considered operational time, the core 
contained significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Small dips 
in neptunium and plutonium number density every 16 years are caused by removing
$^{237}$Np and $^{242}$Pu (included in Processing group ``Higher nuclides'', see
 Table~\ref{tab:reprocessing_list}) which decay into $^{235}$Np and $^{239}$Pu, 
 respectively. Thus, 
production of new fissile materials in the core, as well as $^{233}$U breeding, 
made it possible to compensate for negative effects of strong absorber 
accumulation and keep the reactor critical.
\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{fissile_short.png}
  \caption{Number density of fissile in epithermal spectrum nuclides 
  accumulation during the reactor operation.}
  \label{fig:fissile_short}
\end{figure}

@@

The fuel temperature coefficient (FTC) is negative for both initial and 
equilibrium fuel compositions due to thermal Doppler broadening of the resonance 
capture cross sections in the thorium. A small positive effect of fuel density on 
reactivity increases from $+1.21$ pcm/K at reactor startup to $+1.66$ pcm/K for 
equilibrium fuel composition which has a negative effect on FTC magnitude during the 
reactor operation. This is in good agreement with earlier 
research \cite{robertson_conceptual_1971,park_whole_2015}. The moderator 
temperature coefficient (MTC) is positive for the startup composition and decreases 
during reactor operation because of spectrum hardening with fuel depletion. 
Finally, the total temperature coefficient of reactivity is negative for both 
cases, but decreases during reactor operation due to spectral shift. In 
summary, even after 20 years of operation the total temperature coefficient of 
reactivity is relatively large and negative during reactor operation (comparing 
with conventional PWR which has temperature coefficient about -1.71 pcm/$^\circ$F 
$\approx$ -3.08 pcm/K \cite{forget_integral_2018}), despite positive MTC, and 
affords excellent reactor stability and control.
